\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\title{Life Science Forum of Tsinghua University in 2013}
\date{Oct 19, 2013}

\begin{document}
\maketitle{}

\section{Keynote, Xuetao Cao}
	\subsection{Two different classes of scientist}
		\begin{itemize}
			\item The leading scientists
			\item The exploring scientists
		\end{itemize}
\section{Wu Wei Lab}
	\subsection{Wnt signaling pathway}
		\par
		Build the reporting system of interaction between beta-catenin and TCF, by fluorescence protein fusion method. Beta-catenin protein is bound with half of GFP and TCF protein is bound with the other half of GFP.  Happening the interaction between beta-catenin and TCF, the GFP will be detected using fluorescence microscope.
		\par
		Using IP method to demonstrate that the cyclic anchor of beta-catenin on TCF.
		\par
	\subsection{Cell cycle}
		\par
		Relation between cell cycle and Wnt signaling pathway.
		Wnt signaling is very important in S-G2 phase.
		\par
\section{Meng Anming Lab}
	\par
	The anterior lateral line system is a sensing system of fish. Wnt signaling pathway is important in the leading region, and Fgf signal is essential in the following region.
	\par
	TGF-beta is responsible for cell differentiation and cell proliferation.
	\par
\section{Pan Junmin Lab}
	\par
	Cilia / Flagella is responsible for movement of bacteria. Deficiency of Cilia / Flagella will cause a lot of disease. 
	\par
\section{Du Lijun Lab}
	\par
	Berberine is a chemical in plant, and possibly support blood vesicle protecting.
	\par
\section{Zhou Bin Lab}
	\par
	Huntington Disease results from a copper toxicity and PolyQ. Using Drosophila as a model, the role of two copper transporter has been identified for causing Huntington Disease. P463 Drosophila is a model as a Huntington Disease.
	\par
	The oligomer sate of the Httexon protein may be responsible for the disease happening. Mutation of the protein from copper binding can prevent the fly from Huntington Disease when fed with copper.
	\par
	Copper may bind to Httexon and causing it to aggregate to oligomer state.
\section{Wang Hongwei Lab}
	\par
	The project focuses on the distinct substrate recruitment pathway. The exosome is  involved in RNA maturation. Exosome contains two parts, core domain and Rpn44. Two routes may involved in RNA degradation, through exosome route and direct access route.
	\par
	After EM, 2D and 3D analysis can be done. Different conformation can be observed between exosome with no RNA and with long strand RNA.
	\par
\section{Gong Haipeng Lab}
	\par
	They study the formate transporter in FocA. When importing, FocA using active proton symport mechanism.
	\par
\section{Wang Xinquan Lab}
	\par
	MERS has a fatality of about 50 percent, which is a limited human to human infectious disease.
	\par
\section{Wu Jiawei Lab}
	\par
	Allosteric AMPK regulation is essential for metabolic homeostasis. Gamma subunit is responsible for allosteric regulation. 
	\par
	This most important question is that how AMPK can sense the difference between ATP and ADP. 
	\par
\section{Yang Maojun Lab}
	\par
	Nickel and cobalt is very important for human being. Import of nickel and cobalt is mainly facilitated by an ECF transporter.
	\par
	A new method called XANE can be used to detect the environment around the metal ion.
	\par
\section{Chen Guoqiang Lab}
	\par
	This project focus on a drug on a potential drug agains Alzheimer's Disease. There is an assumption problem of glucose in the brain of an AD patient. HB is a ketone that can prevent the brain. Using the ether form of HB, HBME, may can efficiently prevent from neuron degradation. HBME provides energy and inhibit cell death in deprivation of glucose.
	\par
\section{Deng Haiteng Lab}
	\par
	It  is a proteomics lab. UNG1 is enzyme to cut DNA and initiate DNA repair.
	\par
\section{Liu Dong Lab}
	\par
	The deprivation of phosphate will great damage the growth of the plant. When the soil lacking phosphate, the plant will secrete some acid to turn the organic phosphate to inorganic phosphate.
	\par
	Hsp7 exhibits much shorter root and more root hairs than WT in the Pi starvation condition. Hsp7 mutant will secrete lots of acid.
	\par
\section{Guan Jisong Lab}
	\par
	This lab focuses on memory study.
	\par
\section{Zhang Rongqin Lab}
	\par
	They use \textsl{Pinctada fucata} as model. Matrix protein contains 5 percentage in shells. In vitro expression of pfN44, the protein can be get. PfN44 and the mineral are incubated together, and crystal can be obverses, indicated the association of the protein and the mineral. Beside, with the existence of magnesium ion, pfN44 can inhibit aragonite formation.
\end{document}